$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-05-06 paper/paper.tex
Fix slip
Fix mistake in subject reduction

\begin{note}
  We use $\containsusage{\Gamma}{i}{x}{\Delta}$ to stand for $\contains{\gamma}{\Gamma}{i}{t}{x}{\Delta}$ for some $\gamma$ and $t$.
\end{note}
Subject reduction states that if $P$ is well typed and it reduces to $Q$, then $Q$ is well typed.
In the \picalc{} we distinguish between a reduction $P \reduce{\constr{internal}} Q$ on a channel internal to $P$, and a reduction $P \reduce{\constr{external} \; i} Q$ on a channel $i$ external to $P$ (refer to \autoref{operational-semantics}).
\begin{nitheorem}[Subject reduction]
  Let $P$ be well typed in $\types{\gamma}{\Gamma}{P}{\Xi}$
  \begin{itemize}
    \item If $P \reduce{\constr{internal}} Q$, then $\types{\gamma}{\Gamma}{Q}{\Xi}$.
    \item If $P \reduce{\constr{external} \; i} Q$ and $\containsusage{\Gamma}{i}{\lio}{\Delta}$, then $\types{\gamma}{\Delta}{Q}{\Xi}$.
  \end{itemize}
\end{nitheorem}

\begin{proof}
  By induction on $\types{\gamma}{\Gamma}{P}{\Xi}$.
  \hfill{}\\
  \begin{itemize}
    \item
    Case $\constr{comm}$: we apply framing (\autoref{thm:framing}) to rearrange the assumptions and then apply substitution (\autoref{thm:substitution}) and strengthening (\autoref{thm:strengthening}).

@@

Recent years have seen an increase in the efforts to mechanise resource-aware concurrency calculi, but perhaps one of the earliest works is the mechanisation of the linear \picalc{} in Isabelle/HOL by Gay \cite{Gay2001}.
Gay encodes the \picalc{} with linear and shared types into a more general framework.
As we do, he uses de Bruijn indices, a reduction relation and a type system posterior to the syntax.
However, in his work context splits are explicit, and the types of used multiplicities erased.

>>>>

\begin{note}
  We use $\containsusage{\Gamma}{i}{x}{\Delta}$ to stand for $\contains{\gamma}{\Gamma}{i}{t}{x}{\Delta}$ for some $\gamma$ and $t$.
\end{note}
Subject reduction states that if $P$ is well typed and it reduces to $Q$, then $Q$ is well typed.
In the \picalc{} we distinguish between a reduction $P \reduce{\constr{internal}} Q$ on a channel internal to $P$, and a reduction $P \reduce{\constr{external} \; i} Q$ on a channel $i$ external to $P$ (refer to \autoref{operational-semantics}).
\begin{nitheorem}[Subject reduction]
  Let $P$ be well typed in $\types{\gamma}{\Gamma}{P}{\Xi}$ and reduce such that $P \reduce{c} Q$.
  \begin{itemize}
    \item If $c$ is $\constr{internal}$, then $\types{\gamma}{\Gamma}{Q}{\Xi}$.
    \item If $c$ is $\constr{external} \; i$ and $\containsusage{\Gamma}{i}{\lio}{\Delta}$, then $\types{\gamma}{\Delta}{Q}{\Xi}$.
  \end{itemize}
\end{nitheorem}

\begin{proof}
  By induction on $P \reduce{c} Q$.
  \hfill{}\\
  \begin{itemize}
    \item
    Case $\constr{comm}$: we apply framing (\autoref{thm:framing}) to rearrange the assumptions and then apply substitution (\autoref{thm:substitution}) and strengthening (\autoref{thm:strengthening}).

@@

Recent years have seen an increase in the efforts to mechanise resource-aware concurrency calculi, but perhaps one of the earliest works is the mechanisation of the linear \picalc{} in Isabelle/HOL by Gay \cite{Gay2001}.
Gay encodes the \picalc{} with linear and shared types into a more general framework.
As we do, he uses de Bruijn indices, a reduction relation and a type system posterior to the syntax.
However, in his work context splits are extrinsic, and the types of used multiplicities erased.
